Air cargo load and route planning in pickup and delivery operations

### 2023-07-20 CAIE/caie.tex
CAIE updated and sent to Carlos.
CAIE updated

In this way, the mathematical model for $SolveNode(MIP,\pi_k,G, tmax)$\/ becomes simpler, which finds an allocation of available items at the node $\pi_k$\/ using previously defined values of $L_{\pi_k}$, $T_i^{\pi_k}$, and $a^{\pi_k}_q$. Thus, we use a MIP solver with a runtime limit $tmax$\/ at the node $\pi_k$\/ to maximize the objective function \ref{eq:obj2 with the calculus equations \ref{eq:newf} to \ref{eq:costs2}, subject to the constraints \ref{eq:tau2} to \ref{eq:ifB}. The binary variables $X_{ij}$\/ and $Y_{iq}$\/ define the sets of edges $E_{N_{\pi_k}}$\/ and $E_{Q_{\pi_k}}$, respectively, included in graph $G$.

@@

@@

>>>>

In this way, the mathematical model for $SolveNode(MIP,\pi_k,G, tmax)$\/ becomes simpler, which finds an allocation of available items at the node $\pi_k$\/ using previously defined values of
$L_{\pi_k}$, $T_i^{\pi_k}$, and $a^{\pi_k}_q$.
Thus, we use a MIP solver with a runtime limit $tmax$\/ at the node $\pi_k$ to maximize the objective function \ref{eq:obj2} with the calculus equations \ref{eq:newf} to \ref{eq:costs2}, subject to the constraints \ref{eq:tau2} to \ref{eq:ifB}. The binary variables $X_{ij}$\/ and $Y_{iq}$\/ define the sets of edges $E_{N_{\pi_k}}$\/ and $E_{Q_{\pi_k}}$, respectively, included in graph $G$.

@@

{\color{blue} The dataset used in this study is available in \cite{MesquitaSanches2023}. }

@@

\bibitem{MesquitaSanches2023} Mesquita, Antonio Celio, and Carlos Alberto Alonso Sanches. Air Cargo Load and Route Planning in Pickup and Delivery Operations (2022). Web.
